Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-06-21 ms.tex

\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J.\ E.\  Gizis\altaffilmark{4}, T. Karalidi\altaffilmark{1}, \and J. Teske\altaffilmark{5}}

@@

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
	 [{\bf bottom panels need to be explained; what are y-axis units? why is t1 centered at 0? is this relative to some assumed peak time? what is that time? what about t2?}]}
	\label{fig:ampSpec}
\end{figure*}

@@

\section{Spot Distribution}
\newcommand{\maxSpots}{\#?}

@@

We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.
We allow up to \maxSpots\ {\bf [please fill in]} across the sphere of the brown dwarf, all with a constant temperature contrast.
We set the ``background'' at the measured effective temperature of 1614 K.

>>>>

\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, T. Karalidi\altaffilmark{1}, J.\ E.\  Gizis\altaffilmark{4},  \and J. Teske\altaffilmark{5}}

@@

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
	 {\it Bottom Panels:} The time of maximum variation $t_1$ for each brown dwarf shows no clear trend with wavelength.
	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.
 [{\bf bottom panels need to be explained; what are y-axis units? why is t1 centered at 0? is this relative to some assumed peak time? what is that time? what about t2?}]}
	\label{fig:ampSpec}
\end{figure*}

@@

\section{Spot Distribution}
\newcommand{\maxSpots}{6}

@@

>>>>>>> remotes/origin/sharelatex-2017-06-21-0322
We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.
We allow up to \maxSpots\ {\bf [please fill in]} across the sphere of the brown dwarf, all with a constant temperature contrast.
We set the ``background'' at the measured effective temperature of 1614 K.
